---
title: "Assignment 3"
author: "Cassie Boylan"
date: "`r Sys.Date()`"
output: openintro::lab_report
---
loading libraries needed and importing data
```{r load-packages-data, message=FALSE}
library(tidyverse)
library(RCurl) 
x <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")
```
## Exercise #1
There are 3 majors listed in this data that contain 'DATA' or 'STATISTICS'.  
  
These majors are:  
* MANAGEMENT INFORMATION SYSTEMS AND STATISTICS  
* COMPUTER PROGRAMMING AND DATA PROCESSING  
* STATISTICS AND DECISION SCIENCE  
```{r read-in-csv-file}
majors <- read.csv(text = x)
```

```{r}
data_stat_majors <- grep("DATA|STATISTICS",majors$Major,value=TRUE)
data_stat_majors
```

## Exercise #2  
  
Paste function will concatenate the vectors listed and convert them into datatype character.  This is similar to what c() function does - combines values into a vector & coerces all elements/arguments it is combining into a common type  

Because there are no delimiters being used here, I would use a simpler paste0 which simply concatenates without a separator - like c().  
  
(I am assuming a variable name here as 'fruits')  
  
**paste0(fruits, collapse=NULL)**  
  
  
## Exercise #3  
  
1. will match any string containing a character repeated 3 times in a row
  
2. will match any repeated pair of letters that are **reversed** on 2nd repeat - for example 'anna' or 'deed'.  
  
3. will match any repeated pair of letters  
  
4. will match any string containing a character that occurs 3 times with any random **single**character in between each instance - for example 'anaka' or 'ululu'  
  
5. will match any string containing a set of characters that repeats in reverse with any amount of characters or none in between - for example 'abcdefcba' or 'abccba'  
  
  
## Exercise #4  

 * ^(.).*\1$  
 * (..).*\1
 * (.).*\1.*\1